pdp: An R Package for Creating Partial Dependence Plots

### 2016-09-08 manuscript/greenwell.tex
updated manuscript

Next, we plot the partial dependence of \code{Species} on both \code{Petal.Width} and \code{Petal.Length} for each of the three classes. The result is displayed in Figure~\ref{fig:partial_iris}. Note that we had to supply the original training data to \code{partial} through the \code{train} option. This is necessary for fitted model objects that don't store a copy of the training data (e.g., model fitting functions that don't rely on a formula method).
\begin{example}
pd <- NULL
for (i in 1:3) {
  tmp <- partial(iris.svm, pred.var = c("Petal.Width", "Petal.Length"),
                 which.class = i, .progress = "text",
                 grid.resolution = 101)
  pd <- rbind(pd, cbind(tmp, Species = levels(iris$Species)[i]))
}

@@

To use \code{partial} with the \code{"xgb.Booster"} class, we need to supply the original training data (minus the response!) in the call to \code{partial}. The following snippet of code computes the partial dependence of \code{cmedv} on both \code{rm} and \code{lstat}, individually and together. The results are displayed in Figure~\ref{fig:boston_xgb}. Note that while \code{xgboost} requires the training data to be a matrix (or an object of class \code{"dgCMatrix"} or \code{"xgb.DMatrix"}), \code{partial} requires the training data as a data frame with factors in tact!
\begin{example}
pred.list <- list("lstat", "rm", c("lstat", "rm"))
for (x in pred.list) {
  partial(boston.xgb, pred.var = x, train = subset(boston, select = -cmedv),
          plot = TRUE)
}
\end{example}

@@

\address{Brandon M. Greenwell\\
  Infoscitex Corporation\\
  4027 Colonel Glenn Highway\\
  Suite 210\\
  Dayton, OH 45431-1672\\
  United States of America\\}
\email{bgreenwell@infoscitex.com}

>>>>

Next, we plot the partial dependence of \code{Species} on both \code{Petal.Width} and \code{Petal.Length} for each of the three classes. The result is displayed in Figure~\ref{fig:partial_iris}. Note that we had to supply the original training data to \code{partial} through the \code{train} option. This is necessary for fitted model objects that don't store a copy of the training data (e.g., model fitting functions that don't rely on a formula method).
\begin{example}
pd <- NULL
for (i in 1:3) {
  tmp <- partial(iris.svm, pred.var = c("Petal.Width", "Petal.Length"),
                 which.class = i, grid.resolution = 101, .progress = "text")
  pd <- rbind(pd, cbind(tmp, Species = levels(iris$Species)[i]))
}

@@

To use \code{partial} with the \code{"xgb.Booster"} class, we need to supply the original training data (minus the response!) in the call to \code{partial}. The following snippet of code computes the partial dependence of \code{cmedv} on both \code{rm} and \code{lstat}, individually and together. The results are displayed in Figure~\ref{fig:boston_xgb}. Note that while \code{xgboost} requires the training data to be a matrix (or an object of class \code{"dgCMatrix"} or \code{"xgb.DMatrix"}), \code{partial} requires the training data as a data frame with factors in tact!
\begin{example}
pred.list <- list("lstat", "rm", c("lstat", "rm"))
for (x in pred.list) {
  partial(boston.xgb, pred.var = x, plot = TRUE,
          train = subset(boston, select = -cmedv))
}
\end{example}

@@

\address{Brandon M. Greenwell\\
  Infoscitex Corporation\\
  4027 Colonel Glenn Highway\\
  Suite 210\\
  Dayton, OH 45431-1672\\
  United States of America\\}
\email{greenwell.brandon@gmail.com}
